Plots

### 2021-07-21 02_paper/paper_1/plots_peer/presentation_plots.Rmd
labellist

df_gri_comp <- select(df_gri,
                      !ID)

df_gri_comp <- pivot_longer(data = df_gri,
                            c("DurTOI","M Dur Fix","Number Fix",
                              "TimeTOI Dur","OldGRI","NewGRI","NewGRI_scale"))

df_gri_comp$name <- factor(df_gri_comp$name,
                           levels = c("DurTOI","M Dur Fix","Number Fix",
                                      "TimeTOI Dur","OldGRI","NewGRI",
                                      "NewGRI_scale"),
                           labels = c("Duration TOI","Total dur. of whole fixations (mean)",
                                      "Number of whole fixations","TimeTOI Dur","Old GRI","Adjusted GRI","Adjusted GRI (scaled)")
                           )

ggplot(data = df_gri_comp,
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  labs(y = "",
       x = ""
       ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name), 
             scale = "free")

@@

```{r message=FALSE,warning=FALSE}
ggplot(data = filter(df_gri_comp,
                     TOI == "Calibration phase"),
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  labs(y = "",
       x = ""
       ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name), 
             scale = "free")
```
## Novice vs. Expert (Asking Question)

@@

df_table <- tibble(Value = c("GRI","Adj. GRI","Adj. GRI (scale)"),
                   Mean = c(mean(df_gri$OldGRI),mean(df_gri$NewGRI),mean(df_gri$NewGRI_scale)),
                   SD = c(sd(df_gri$OldGRI),sd(df_gri$NewGRI),sd(df_gri$NewGRI_scale)),
                   Median = c(median(df_gri$OldGRI),median(df_gri$NewGRI),median(df_gri$NewGRI_scale))
                   )

@@

knitr::kable(df_table)

>>>>

df_gri_comp <- select(df_gri,
                      !c(ID,`M Dur Fix`))

df_gri_comp <- pivot_longer(data = df_gri_comp,
                            c("DurTOI","Number Fix",
                              "TimeTOI Dur","OldGRI","NewGRI","NewGRI_scale"))

df_gri_comp$name <- factor(df_gri_comp$name,
                           levels = c("DurTOI","Number Fix",
                                      "TimeTOI Dur","OldGRI","NewGRI",
                                      "NewGRI_scale"),
                           labels = c("Duration TOI",
                                      "Number of whole fixations","TimeTOI Dur","Old GRI","Adjusted GRI","Adjusted GRI (scaled)")
                           )

ggplot(data = filter(df_gri_comp,
                     TOI != "Calibration phase"),
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  labs(y = "",
       x = ""
       ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name), 
             scale = "free")

@@

```{r message=FALSE,warning=FALSE}
ggplot(data = filter(df_gri_comp,
                     TOI == "Calibration phase"),
       mapping = aes(x = Group,
                     y = value
                     )
       ) +
  geom_boxplot(mapping = aes(fill = Group)) +
  geom_point(size = 2, 
             alpha = 0.4,
             position = position_jitter(seed = 1, 
                                        width = 0.1
                                        )
             ) +
  labs(y = "",
       x = ""
       ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_clean() +
  facet_wrap(vars(name), 
             scale = "free")
```

## Novice vs. Expert (Asking Question)

@@

df_gri_n <- filter(df_gri,
                   Group == "Novice",
                   TOI != "Calibration phase")

df_table_n <- tibble(Value = c("GRI","Adj. GRI","Adj. GRI (scale)"),
                   Mean = c(mean(df_gri_n$OldGRI),mean(df_gri_n$NewGRI),mean(df_gri_n$NewGRI_scale)),
                   SD = c(sd(df_gri_n$OldGRI),sd(df_gri_n$NewGRI),sd(df_gri_n$NewGRI_scale)),
                   Median = c(median(df_gri_n$OldGRI),median(df_gri_n$NewGRI),median(df_gri_n$NewGRI_scale))
                   )

df_gri_e <- filter(df_gri,
                   Group == "Expert",
                   TOI != "Calibration phase")

df_table_e <- tibble(Value = c("GRI","Adj. GRI","Adj. GRI (scale)"),
                   Mean = c(mean(df_gri_e$OldGRI),mean(df_gri_e$NewGRI),mean(df_gri_e$NewGRI_scale)),
                   SD = c(sd(df_gri_e$OldGRI),sd(df_gri_e$NewGRI),sd(df_gri_e$NewGRI_scale)),
                   Median = c(median(df_gri_e$OldGRI),median(df_gri_e$NewGRI),median(df_gri_e$NewGRI_scale))
                   )

@@

knitr::kable(df_table_n,
             caption = "Experts")

knitr::kable(df_table_e,
            caption = "Novice")
